\cvsection{Education}
\begin{cventries}
  \cventry
    {MSc Artificial Intelligence}
    {The University of Edimburgh}
    {Edimburgh, UK}
    {Sep. 2019 - Aug. 2020}
    {
      \begin{cvitems}
        \item {Master of Science focused on Artificial Intelligence and Cognitive Science.}
      \end{cvitems}
    }
    
  \cventry
    {\href{http://www.manchester.ac.uk/study/undergraduate/courses/2017/00517/bsc-artificial-intelligence/}{BSc in Artificial Intelligence with Industrial Experience}}
    {\href{www.manchester.ac.uk}{The University of Manchester}}
    {Manchester, UK}
    {Sep. 2015 - Jun. 2019}
    {
      \begin{cvitems}
        \item {\textbf{Final result: 1st Class Degree (78.6\%)}}
        % \item {Achieved a first class grade in all the courses of the first year.}
        % \item {Particularly enjoyed Object Oriented Programming (Java), Fundamentals of Artificial Intelligence and Fundamentals of Computation.}
        % \item {Strong interest in theoretical Computer Science, in particular Computability Theory, and AI.}
        \item {Modules taken include Machine Learning and Optimisation, Computer Vision, Natural Language Systems, Symbolic AI, Statistics, Advanced Algorithms, Logic and Modelling, Advanced Computer Graphics, Image Processing and Mobile Systems.}
      \end{cvitems}
    }
    \begin{cvsubentries}
      \cvsubentry{Third Year Project}
      {Spiking Neural Network Shape Detector}
      {2018/2019}
      {Developed a biologically inspired Spiking Neural Network which can be used to recognise and track simple shapes moving in a video stream in real time. The network presented runs in biological real time on a 4 chips SpiNNaker board, a type of low energy neuromorphic supercomputer.}
    \end{cvsubentries}

    \begin{cvsubentries}
      \cvsubentry{\href{www.stendhalgame.org}{stendhalgame.org}}
      {Stendhal Game}
      {2016}
      {As part of 2nd Year Software Engineering I have tested, debugged, built, developed and deployed a multi-user, multi-threaded, client-server open source game containing over 6000 Java classes and 1800 test cases using Eclipse, Git, Apache Ant, Jenkins and JUnit.}
    \end{cvsubentries}

    \begin{cvsubentries}
      \cvsubentry{}{FestivalFinder}
      {2016}
      {\em{Won the ”Best use of Data” in the First Year projects competition.} Built as First Year Team Project FestivalFinder a festival finder website both for web platform and mobile.}
    \end{cvsubentries}

    \cventry
      {Scientific Curriculum High School}
      {\href{https://www.messedaglia.gov.it/}{Liceo Scientifico Statale ``A. Messedaglia''}}
      {Verona, Italy}
      {Sep. 2010 - Jul. 2015}
      {
        \begin{cvitems}
          \item {\textbf{Final result: 100\%} --- Final personal project on Artificial Intelligence: \em{“Mathematical and logical limits to AI”}.}
          % \item {Final personal project on Artificial Intelligence: \em{“Mathematical and logical limits to AI”}.}
          % \item {The results of both my final year report and exam had been published on the local newspaper.}
          % \item {Strong interest in Mathematics and Philosophy, both helped to choose Artificial Intelligence as a degree.}
        \end{cvitems}
      }
\end{cventries}
