\cvsection{Experience}
\begin{cventries}

  \cventry
  {Software Developer Intern}
  {\href{http://www.dodifferent.it/}{Do Different srl}}
  {Verona, Italy}
  {Jul. 2016 - Aug. 2016}
  {
    \begin{cvitems}
      \item {Six weeks paid summer internship.}
      \item {Edited the HTML/CSS front-end of a web app developed by Do Different introducing new functionalities.}
      \item {Written and updated documentation for a Master Data Management software developed for a large insurance company in Java EE and Oracle SQL.}
      \item {Worked on a insurance loyalty website developed with Java EE and Primefaces. During the bugfix phase I completed my assigned task earlier than expected.}
      \item {Worked for three weeks on an banking Android app developed by another studio and given to Do Different at a later stage. I updated the front-end to the new graphical requirements and integrated it with the new functionalities required in the back end.}
      \item {During the internship I had the chance to improve my understanding of git and my interpersonal, presentation and communications skills working in a 15-people team spread between Milan and Verona and having daily meetings with my supervisor.}
    \end{cvitems}
  }

  \cventry
  {Summer Intern as ``Yellow Shirt''}
  {\href{http://www.ces-schools.com}{Centre of English Studies}}
  {Dublin, Ireland}
  {Aug. 2014 - Aug. 2014}
  {
    \begin{cvitems}
      \item {Two weeks summer internship.}
      \item {My role was to organise and lead the students of the Centre of English Studies in the afternoon activities like visits to museums or the countryside.}
      \item {I worked in a team, this gave me the chance to improve my organisational and communications skills. I also had to report on a daily basis to my supervisor.}
    \end{cvitems}
  }

  \cventry
  {Summer Intern}
  {\href{http://www.aerlybirdtransglobal.com}{Aerly Bird Trans Global}}
  {Dublin, Ireland}
  {Jul. 2014 - Jul. 2014}
  {
    \begin{cvitems}
      \item {Two weeks summer internship.}
      \item {I used the company Database software to handle information about shipping.}
      \item {I improved my attention to details and my communications skills through working regularly in teams.}
    \end{cvitems}
  }

  \cventry
  {Summer Intern}
  {\href{http://www.techne.it/}{Techne Media Agency}}
  {Verona, Italy}
  {Jun. 2013 - Jun. 2013}
  {
    \begin{cvitems}
      \item {Two weeks summer internship.}
      \item {I used the software developed by the company to research about the use of social media marketing by international and Italian brands.}
      \item {The software I used was developed by the company and I demonstrated an ability to learn quickly. I also organised a presentation for some of the managers with the results of my researches.}
    \end{cvitems}
  }

\end{cventries}
